Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/desiderata.tex
minor desiderata changes

The interesting (and difficult) case is satisfying {\it both} desiderata. To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

>>>>

The interesting (and difficult) case is satisfying {\it both} desiderata. To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.
